\begin{recipe}{Ken's Granola}{half-sheet pan \hfill 250\0F \hfill 2 hrs.}{\textbf{Source:} Ken Bieber \hfill serves 8}
 \freeform [CB] This recipe has different proportions to \hyperref[Granola]{Granola}; perhaps you prefer it!

 \ing[3]{cups}{rolled oats}
 \ing[1]{cup}{wheat germ}
 \ing[1]{cup}{sesame seeds and/or nuts}
 \ing[\fr12]{cup}{(shredded coconut)}
 \ing[\fr12]{cup}{bran}
 \ing[\fr14]{cup}{oil}
 \ing[\fr34]{cup}{honey, molasses, or corn syrup}
 Mix all ingredients together. Spread \fr12\inch deep in a large baking pan.

 \newstep Bake until golden brown, stirring occasionally. Remove and cool. Add [1 cup] raisins, dates, and/or dried fruits. Store in [airtight] jars.
\end{recipe}

\begin{recipe}{Sourdough Starter}{}{\textbf{Source:} Ann Williams \hfill }
 \ing[2]{medium}{potatoes, cubed}
 \ing[3]{cups}{water}
 Boil potatoes until tender. Remove potatoes for another use, reserving the broth.

 \ing[2]{cups}{potato broth}
 \ing[2]{cups}{flour}
 \ing[1]{tbsp.}{sugar}
 Cool potato broth to lukewarm. Mix with flour and sugar to form a smooth paste. Set in a warm place until starter rises to double its original size.
\end{recipe}

\begin{recipe}{Sourdough Biscuits}{8\inch round pan \hfill 425\0F \hfill [15 min.]}{\textbf{Source:} Ann Williams \hfill serves 8}
 \ing[3]{cups}{flour}
 \ing[1]{tsp.}{salt}
 \ing[1]{tsp.}{sugar}
 \ing[1]{tsp.}{baking soda}
 Sift dry ingredients into a large mixing bowl.

 \ing[1]{cup}{\hyperref[Sourdough Starter]{sourdough starter}}
 \ing[1]{tbsp.}{shortening, melted}
 Make a well in the center of the flour and add the sourdough starter and shortening. Mix well, adding more flour (up to 1 cup) to make a stiff dough.

 \ing[1--2]{tbsp.}{shortening, melted}
 Pinch off a biscuit's worth of dough, roll it into a ball and coat in melted shortening. Crowd the biscuits in a round pan and let rise in a warm place for 20--30 min. Bake until done [golden].
\end{recipe}

\begin{recipe}{Goulash}{frying pan \hfill 1 hr.}{\textbf{Source:} Ken Bieber \hfill serves 4}
 \freeform [CB] This recipe has two variants, one with pork and one with veal.

 \ing[1]{medium}{onion, chopped}
 \ing[2]{tbsp.}{butter}
 \ing[1]{tbsp.}{paprika}
 \ing[1]{tsp.}{salt}
 Saute onion in butter until brown. Stir in paprika and salt.

 \ing[1]{}{green pepper, chopped}
 \ing[1]{}{tomato, chopped}
 \ing[1]{lb.}{veal, cubed}
 Add vegetables and meat and fry gently until meat changes color.

 \ing[2]{tsp.}{flour}
 \ing[5]{oz.}{stock (1 broth cube)}
 Remove pan from heat and stir in flour, then gradually add stock. Return to a boil and simmer gently until meat is tender, \~45 min.

 \ing[5]{oz.}{yogurt}
 Just before serving, blend in yogurt and season as desired. Serve over macaroni.

 \freeform Notes:
 \begin{itemize}
  \item To make pork goulash, substitute 2--3 cups cubed cooked pork for the veal and 2 cups sauerkraut for the vegetables. Season with 1 tbsp.\ caraway.
 \end{itemize}
\end{recipe}

\begin{recipe}{Sweet \& Sour Cabbage}{ \hfill stovetop \hfill 10 min.}{\textbf{Source:} Natural Foods Cookbook \hfill serves 6}
 \ing[4]{cups}{cabbage, shredded}
 \ing[3]{}{onions, grated}
 \ing[2]{}{lemons, juiced}
 \ing[4]{}{tart apples, diced}
 \ing[\fr12]{cup}{seedless raisins}
 \ing[\fr14]{cup}{sweet cider}
 \ing[3]{tbsp.}{honey}
 \ing[2]{tbsp.}{oil}
 \ing[1]{tbsp.}{caraway seeds}
 \ing[]{pinch}{ground allspice}
 Combine all ingredients in a large saucepan. Cover and simmer gently for 10 min.
\end{recipe}

\begin{recipe}{Curried Eggs}{ \hfill stovetop \hfill 15 min.}{\textbf{Source:} Ken Bieber \hfill serves 3--6}
 \ing[4]{tbsp.}{butter}
 \ing[\fr12]{cup}{onion, chopped}
 \ing[1]{clove}{garlic, minced}
 Saute onion and garlic in butter.

 \ing[1]{tbsp.}{curry powder}
 \ing[1]{tsp.}{tomato paste}
 Blend in curry powder and tomato paste and cook for 1 min.

 \ing[1\fr12]{cup}{milk}
 Gradually add milk, stirring constantly. Cook on low for 10 min.

 \ing[6]{}{eggs, hardboiled \& peeled}
 \ing[1]{tsp.}{salt}
 Add salt and eggs. Serve.
\end{recipe}

\begin{recipe}{Toasted Seeds}{half-sheet pan \hfill 250\0F \hfill 30 min.}{\textbf{Source:} Ken Bieber \hfill }
 \ing[]{}{seeds: melon, pumpkin, squash, sunflower}
 Clean fiber from fresh seeds. Cover with salted water, bring to a boil, and simmer for 2 hrs.

 \newstep Drain boiled seeds, dry on paper towels, then deep-fry or roast in the oven: coat with oil, sprinkle with salt, stir occasionally.

 \freeform Notes:
 \begin{itemize}
  \item [CB] We roast squash seeds more simply: clean \& rinse seeds, lightly oil and salt, bake at 400\0F in a single layer for 10--15 min. or until lightly browned.
 \end{itemize}
\end{recipe}

\begin{recipe}{Oven-Roasted Potatoes}{9\inch\X13\inch baking dish \hfill 350\0F \hfill 1.5 hrs.}{\textbf{Source:} Madhu Bieber \hfill serves 6}
 \ing[\fr12]{cup}{butter}
 Place butter in a shallow baking dish. Heat in the oven until butter is melted.

 \ing[6--8]{medium}{potatoes, peeled}
 \ing[\fr12]{tsp.}{salt}
 \ing[]{dash}{pepper}
 Roll potatoes in melted butter. Sprinkle with salt and pepper. Cover pan tightly with foil. Return to oven and bake 1\fr14 hrs.

 \ing[1]{tsp.}{paprika}
 \ing[2]{tsp.}{(parsley, chopped)}
 Transfer potatoes to serving dish and pour over butter from baking dish. Sprinkle with paprika and parsley, if desired.

 \freeform Notes:
 \begin{itemize}
  \item If dinner is delayed, remove foil and continue baking potatoes up to 30 min.\ longer. They will brown attractively.
 \end{itemize}
\end{recipe}

\begin{recipe}{Broiled Potatoes}{broiling rack \hfill 20 min.}{\textbf{Source:} Madhu Bieber \hfill serves 4}
 \ing[3]{medium}{potatoes}
 Scrub potatoes but do not peel. Cut into \fr14\inch crosswise slices.

 \ing[\fr13]{cup}{oil}
 \ing[\fr12]{tsp.}{salt}
 \ing[]{}{paprika, to taste}
 Dip slices in oil and place in a single layer on broiler rack. Sprinkle with salt and paprika.

 \newstep Broil until potatoes are golden brown on one side, \~7 min. Flip and continue boiling until brown. Serve hot.
\end{recipe}

\begin{recipe}{Delicious Mashed Potatoes}{ \hfill 10 min.}{\textbf{Source:} Madhu Bieber \hfill serves 4}
 \ing[4]{servings}{instant mashed potatoes}
 Prepare potatoes as directed on package, omitting butter.

 \ing[\fr12]{cup}{sour cream}
 \ing[\fr14]{tsp.}{onion salt}
 \ing[]{dash}{black pepper}
 Stir in sour cream, onion salt, and pepper. Heat until piping hot and serve.
\end{recipe}

\begin{recipe}{Hash-Browned Onion Potatoes}{large skillet \hfill stovetop \hfill 30 min.}{\textbf{Source:} Madhu Bieber \hfill serves 8}
 \ing[8]{cups}{potatoes, cubed}
 \ing[\fr14]{cup}{butter}
 Lightly brown potatoes in butter in a large skillet.

 \ing[1]{pkg.}{onion soup mix (1.5 oz.)}
 \ing[1]{cup}{water}
 Add onion soup mix and water. Cover and simmer, stirring occasionally, until potatoes are tender, \~10 min. Uncover and cook a few minutes more until liquid is absorbed. Serve.
\end{recipe}

\begin{recipe}{Swiss Potatoes}{large skillet \hfill stovetop \hfill 15 min.}{\textbf{Source:} Madhu Bieber \hfill serves 4}
 \ing[1]{lb.}{whole white potatoes (1 can)}
 \ing[2]{tbsp.}{bacon drippings or shortening}
 \ing[1]{small}{onion, chopped}
 Drain potatoes and chop fine. Cook with onion in hot fat until crisp and browned, stirring occasionally.

 \ing[\fr12]{tsp.}{salt}
 \ing[\fr18]{tsp.}{pepper}
 Season with salt and pepper, and serve.
\end{recipe}

\begin{recipe}{Potato-Sausage Skillet}{large skillet \hfill stovetop \hfill 30 min.}{\textbf{Source:} Madhu Bieber \hfill serves 6}
 \ing[9]{oz.}{frozen hash browns (\fr12 pkg.)}
 Prepare potatoes as directed on package. Drain well.

 \ing[\fr12]{lb.}{pork sausages}
 \ing[1]{cup}{onion, chopped}
 Saute onion and sausage together until sausage browns. Drain off all but \fr14 cup fat.

 \ing[\fr12]{tsp.}{salt}
 \ing[\fr14]{tsp.}{celery salt}
 \ing[\fr14]{tsp.}{ground sage}
 \ing[\fr18]{tsp.}{pepper}
 Add potatoes and seasonings. Cook, stirring occasionally, until golden brown.
\end{recipe}

\begin{recipe}{Baked Creamed Potatoes}{8\inch\X8\inch baking dish \hfill 350\0F \hfill 20--25 min.}{\textbf{Source:} Madhu Bieber \hfill serves 6}
 \ing[1]{cup}{sour cream}
 \ing[\fr12]{cup}{milk}
 \ing[1]{tbsp.}{onion powder}
 \ing[1]{tsp.}{parsley flakes}
 \ing[1]{tsp.}{salt}
 \ing[\fr18]{tsp.}{pepper}
 Mix sour cream, milk, and seasonings in a bowl.

 \ing[5]{cups}{potatoes, cooked \& sliced}
 Place half the potatoes in a greased baking dish. Top with half the cream sauce. Repeat with another layer of potatoes, then sauce.

 \ing[\fr12]{cup}{Cheddar cheese, grated}
 Sprinkle cheese over top. Bake until bubbly and browned.
\end{recipe}

\begin{recipe}{Two-Step Potatoes}{8\inch\X8\inch baking dish \hfill 350\0F \hfill 1 hr.}{\textbf{Source:} Madhu Bieber \hfill serves 6}
 \ing[12]{medium}{red potatoes}
 Boil unpeeled potatoes in water until almost tender, but still firm. Cool, peel, and shred with a wide grater. You should have \~4\fr12 cups of potatoes.

 \ing[1]{tsp.}{salt}
 \ing[\fr14]{tsp.}{pepper}
 \ing[\fr12]{tsp.}{onion or garlic salt}
 \ing[\fr12]{cup}{mild Cheddar cheese, grated}
 Grease a square baking dish and cover bottom with half the potatoes. Sprinkle with half the seasonings and top with half the cheese. Repeat with another layer of potatoes, seasonings, and cheese.

 \ing[1]{cup}{heavy cream}
 Pour cream over top. Bake until browned, about 1 hr.
\end{recipe}

\begin{recipe}{Potatoes Chantilly}{8\inch\X8\inch baking dish \hfill 350\0F \hfill 20 min.}{\textbf{Source:} Madhu Bieber \hfill serves 4--6}
 \ing[1]{pkg.}{instant mashed potatoes (4 servings)}
 Prepare potatoes as directed on package. Place in a greased baking dish.

 \ing[1]{cup}{heavy cream}
 \ing[\fr12]{cup}{sharp Cheddar cheese, grated}
 Whip cream; fold in cheese. Season with salt and pepper to taste. Spread over potatoes. Bake until golden and serve immediately.
\end{recipe}

\begin{recipe}{Oven-Fried Potatoes}{2 half-sheet pans \hfill 450\0F \hfill 20--25 min.}{\textbf{Source:} Madhu Bieber \hfill serves 6}
 \ing[5]{medium}{potatoes, scrubbed}
 Cut potatoes into \fr14\inch crosswise slices.

 \ing[\fr23]{cup}{oil}
 Pour half the oil into each baking tray. Add potatoes, turning them to evenly coat with oil. Arrange potatoes into a single layer.

 \newstep Bake until potatoes are lightly browned. Sprinkle with salt and pepper and serve hot.
\end{recipe}

\begin{recipe}{Cheese French Fries}{half-sheet pan \hfill 400\0F \hfill 15 min.}{\textbf{Source:} Madhu Bieber \hfill serves 6}
 \ing[18]{oz.}{frozen French fries (2 pkgs.)}
 \ing[1]{tsp.}{onion salt}
 \ing[\fr14]{tsp.}{paprika}
 Place potatoes in a shallow baking tray. Sprinkle with salt and paprika. Bake as directed on package.

 \ing[\fr13]{cup}{Parmesan cheese, grated}
 Sprinkle with cheese, shaking pan to coat evenly. Serve immediately.
\end{recipe}

\begin{recipe}{Corn \& Potato Chowder}{2qt. saucepan \hfill stovetop \hfill 30 min.}{\textbf{Source:} anon. clipping \hfill serves 6--8}
 \ing[1\fr12]{cups}{potatoes, peeled \& cubed}
 \ing[1]{cup}{water}
 \ing[\fr14]{tsp.}{salt}
 Boil potatoes in salted water for 8--10 min. Drain, reserving the broth.

 \ing[3]{tbsp.}{butter}
 \ing[\fr12]{cup}{onion, chopped}
 \ing[\fr12]{cup}{celery, chopped}
 Saute onion and celery in butter until celery is cooked, 5 min.

 \ing[1\fr12]{tbsp.}{flour}
 Remove pan from heat and add flour, stirring vigorously. Cook on low until bubbling.

 \ing[2]{cups}{milk}
 Stir in potato broth and milk. Bring to a boil and hold for 1 min., stirring constantly.

 \ing[14]{oz.}{creamed corn (1 can)}
 \ing[\fr14]{tsp.}{salt}
 \ing[\fr14]{tsp.}{(white) pepper}
 \ing[1]{tsp.}{(parsley, chopped)}
 Stir in corn, potatoes, salt, and pepper. Heat through and serve, sprinkled with parsley.
\end{recipe}

\begin{recipe}{Zucchini Nut Bread}{8\fr12\inch\X4\fr12\inch loaf pans \hfill 350\0F \hfill 1 hr.}{\textbf{Source:} Anonymous \hfill makes 2 loaves}
 \ing[3]{cups}{flour}
 \ing[1\fr12]{tsp.}{ground cinnamon}
 \ing[1]{tsp.}{baking soda}
 \ing[1]{tsp.}{salt}
 \ing[\fr14]{tsp.}{baking powder}
 Sift dry ingredients together in a medium bowl.

 \ing[3]{}{eggs}
 \ing[1\fr12]{cups}{sugar}
 \ing[1]{cup}{oil}
 \ing[1]{tbsp.}{vanilla extract}
 Beat eggs in a large mixing bowl. Gradually add sugar, oil, and vanilla, mixing well. Add dry ingredients and mix well.

 \ing[2]{cups}{zucchini, grated}
 \ing[\fr12]{cup}{walnuts, chopped}
 Stir in zucchini and walnuts. Pour into greased loaf pans. Bake 1 hr. [or until a toothpick comes out clean]. Remove from pan and cool on racks before serving.
\end{recipe}

\begin{recipe}{Zucchini Loaf}{8\fr12\inch\X4\fr12\inch loaf pan \hfill 375\0F \hfill 50--60 min.}{\textbf{Source:} \hfill makes 1 loaf}
 \ing[\fr34]{cup}{whole wheat or all-purpose flour}
 \ing[\fr34]{cup}{rolled oats}
 \ing[\fr12]{tsp.}{baking powder}
 \ing[\fr12]{tsp.}{baking soda}
 \ing[\fr12]{tsp.}{salt}
 \ing[\fr34]{tsp.}{ground cinnamon}
 Sift dry ingredients together in a medium bowl.

 \ing[2]{}{eggs}
 \ing[\fr34]{cup}{brown sugar}
 \ing[\fr12]{cup}{oil}
 Beat eggs, sugar, and oil in a large bowl until thoroughly combined. Add dry ingredients and mix well.

 \ing[1\fr14]{cup}{zucchini, grated}
 \ing[\fr12]{cup}{nuts, chopped}
 \ing[1]{tbsp.}{(sesame seeds)}
 Stir in zucchini and nuts. Pour into greased loaf pan and sprinkle with sesame seeds. Bake for 50--60 min. or until a toothpick comes out clean.
\end{recipe}

\begin{recipe}{Apple Gingerbread Flan with Lemon Custard}{9\fr12\inch springform pan \hfill 350\0F \hfill 1 hr.}{\textbf{Source:} Brenda Blais, West End Vegetarian Restaurant \hfill serves 12}
 \freeform [CB] This recipe comes from a Toronto restaurant, reprinted in Starweek by reader request. It sounds amazing.

 \ing[2]{cups}{unbleached white flour}
 \ing[1]{cup}{brown sugar}
 \ing[2]{tsp.}{baking powder}
 \ing[\fr14]{tsp.}{baking soda}
 \ing[2]{tsp.}{ground ginger}
 \ing[\fr12]{tsp.}{ground cinnamon}
 \ing[\fr18]{tsp.}{ground cloves}
 \ing[\fr18]{tsp.}{ground allspice}
 \ing[\fr18]{tsp.}{pepper}
 \ing[\fr18]{tsp.}{salt}
 In a large/mixing bowl, sift together the dry ingredients.

 \ing[2]{}{eggs}
 \ing[6]{tbsp.}{butter, melted}
 \ing[2]{tbsp.}{molasses}
 In a smaller bowl, mix the wet ingredients. Add them to the dry mixture and stir or mix until well blended.

 \ing[4]{large}{apples, peeled \& sliced}
 \ing[\fr14]{tsp.}{ground ginged}
 Pour the gingerbread into a well-greased cake pan. Arrange the apples in a circle on top of the batter and sprinkle the ginger over top. Bake for 30 min.

 \ing[\fr12]{cup}{brown sugar}
 \ing[2]{}{eggs}
 \ing[\fr14]{cup}{whipping cream}
 \ing[4]{tbsp.}{lemon juice}
 \ing[2]{tbsp.}{lemon zest}
 \ing[4]{tbsp.}{butter, melted}
 While the base bakes, whisk together the custard ingredients. Pour this mixture over the cake and bake for another 20--25 min.

 \newstep Cool to room temperature before removing from the pan.
\end{recipe}
