\begin{recipe}{Veggie Chili}{pressure cooker \hfill stovetop \hfill 1.5 hrs.}{serves 8}

 \freeform This recipe is very flexible, so use a mix of beans and vegetables that suits you! As written it is fairly mild.

 \ing[2--3]{cups} {dry beans: black, kidney, white, garbanzo}
 Start beans in the pressure cooker. While they cook, chop vegetables, bake cornbread, and/or start rice cooking.

 \ing[1--2]{tbsp.}{cumin}
 \ing[1--2]{tbsp.}{coriander}
 \ing{}{dried red pepper, to taste}
 Optional: Toast whole spices in a skillet. When they smell good, grind them in the mortar.

 \ing[2]{}{onions, peeled and chopped}
 \ing[6--10]{cloves}{garlic, peeled and chopped}
 \ing[3]{}{carrots}
 \ing[1]{}{green pepper}
 Saute onions, garlic, carrots, and spices (if not previously toasted) in a skillet. When the onion is brown, add the green peppers.

 \ing[\fr{12}]{cup}{wine or beer}
 \ing[28]{oz.}{diced tomatos (any flavor)}
 \ing[2]{tbsp.}{oregano}
 \ing[2]{tbsp.}{basil}
 \ing[1]{cup}{(TVP)}
 When vegetables have started to soften, add the skillet contents, herbs, and canned tomatos to the beans. Deglaze the skillet with wine, beer, or tomato juice and add the results to the beans. Stir and return to a simmer.

 \newstep Simmer the chili until the flavors and consistency are correct or your patience runs out. Add wine, water, or stock if it's too dry; add TVP or boil down if it's too wet. Salt, then add more of whatever's needed: tomato paste, hot sauce / chipotle, cocoa powder\dots

 \newstep Serve chili in bowls, with grated cheese, yogurt, cornbread, and/or rice.

 \freeform Notes:
 \begin{itemize}
  \item 1--2 cups frozen corn can go in any time. Kale or other greens should go in 5--10 minutes before serving.
  \item If you want to use canned beans, aim for 6 cups cooked beans total---3 large cans should do it.
 \end{itemize}
\end{recipe}
