% TODO
% straighten out section heading format (centered? nonumber?), ToC numbering, recipe numbering
% refine recipe template lines, vspacing, page breaks, dingbats between recipes? overfull boxes
% transcribe the rest of what I have collected already;
% figure out presentation for menus, online recipes, and longer prose
% add pictures of e.g. well-fried tofu?
% add options to cb_cuisine for horizontal, vertical, and inline (Joy) format
% write a parser (?) to translate tex to rmd and vice versa (?)
% figure out booklet layout?
% figure out input{*}??
% place steps inside ingredient boxes so \newstep takes less vertical space?
% can pdflatex figure out the optimum recipe column widths based on the contents???
% keep fixing index format
% consider removing non-oven cooking times entirely; moving "chopped" into steps

\documentclass{article}
\usepackage{cb_recipe}
\usepackage{imakeidx}
\usepackage[hyperindex,colorlinks]{hyperref}
\makeindex

\begin{document}
\tableofcontents

\begin{itemize}
 \item Passover and Thanksgiving;
 \item Allan’s cookbooks v1 & v2;
 \item food I’ve photographed & bookmarked;
 \item Daniel’s recipe notes
 \item recipes from our !wedding??
 \item guest recipes for Indian delicacies??
\end{itemize}

\section{Introduction}
concept: family recipes, stuff we cook a lot, techniques/etc. we don't see often, stuff we want to pass down

\begin{itemize}
 \item philosophy of this book and how we cook: We use vegetable oil by default, with butter and olive oil for flavor and extra-virgin olive oil for salads/drizzling. I habitually cut the sugar in half when baking. We never peel vegetables unless they're coated in wax, like turnips; I'd rather roast unpeeled squash and scoop out the skins than peel them. We grow basil, oregano, sage, mint, and rosemary in window baskets.

       Our kitchen is equipped with 2 cast iron skillets and a Dutch oven; 1 large soup pot; 1 huge stock / beer pot; 1 medium and 1 small saucepans; 1 huge electric griddle; 1 set of Pyrex mixing bowls; 2 aluminum half-sheet pans; 1 set of Pyrex baking dishes (loaf, square, rectangle); a stand mixer, a food processor, a stick blender w/ whisk attachment, a pastry blender; 2 large, 2 medium, 1 paring, and 1 bread knife;

 \item how to roast veges
 \item how to saute tofu, potatos, and veges
 \item tips on tofu, tempeh, seitan
 \item cast iron
 \item salad dressing in general? mustard? etc.
\end{itemize}

\subsection{Cookbooks We Love}
\begin{itemize}
 \item Moskowitz, Veganomicon
 \item Bittman, How To Cook Everything Vegetarian
 \item Iyer, 660 Curries
 \item Ottolenghi, Plenty
 \item 330 Vegetarian Recipes
 \item Joy of Cooking
 \item Julia Child, Vol. 1
 \item Brown, Tassajara
 \item Reinhart’s bread book
 \item Katzen, Moosewood
 \item Gaia’s Kitchen
\end{itemize}

\subsection{Online Recipes}
(just links & annotations?)(prepended to their respective sections?)
\begin{itemize}
 \item SE pressure cooker tomato sauce
 \item SE risotto
 \item SE crispy potatos
 \item \href{https://smittenkitchen.com/2016/01/ugly-but-good-cookies/}{SK ugly but good cookies} (nutella meringues, Passover 2018)
 \item SK chewy amaretti cookies (Passover 2017)
 \item SK apple cakes
 \item \href{https://smittenkitchen.com/2010/05/carrot-salad-with-harissa-feta-and-mint/}{SK carrot harissa salad}
 \item SK miso-tahini dressing
\end{itemize}

\subsection{How To Read These Recipes}
The title of each recipe includes a summary on how the dish is cooked. Special equipment (e.g. cast iron skillet, 9\inch\x13\inch baking dish, stand mixer) are called out. If the oven is used, the temperature and baking time are listed; in all other cases, the time given is an estimate of the active cooking time. Temperatures are given in Fahrenheit and measurements are given in Imperial. Ingredients listed in () are optional.

I encourage you to read the entire recipe through before you start! I've tried to indicate where prep can happen in parallel but you know your own process best.

While I've tried to respect the source recipes, I've taken license to paraphrase and streamline them during transcription. The originals are available in digital and analog format as an appendix.

\section{Vegan}
how we veganize things
vegan bechamel
tofu scramble from Max
\href{http://sabotabby.livejournal.com/1344653.html}{vegan Nanaimo bars}
\href{http://sabotabby.livejournal.com/1372333.html}{vegan millionaires}
vegan latkes
avocado pie from Max??
vegan matzo balls?
\input{vegan}

\section{Breakfast}
% \input{}
\input{breakfast/granola}
\input{breakfast/fritatta}
\input{breakfast/oatmeal}
Pancakes \& Waffles
clafoutis/dutch pancake

\section{Soups \& Stews}
\input{dinner/chili}
Zucchini Rosemary Soup (MW)
Mushroom Barley Soup (MW)
potato chickpea curry
curry squash soup

\section{Bread}
 (Phil’s bread recipes?)
Daniel’s bread recipes?
skillet cornbread
biscuits

\section{Entrees}
tempeh pasta from Veganomicon
butternut-miso pasta sauce from Steph
tofu salad from Katzen
peanut noodles from Katzen
Bengali kitchiri

\section{Sides \& Snacks}
candied carrots
greens w/ garlic
couscous w/ fruit & nuts (or biryani)
pakoras
rice crispie snack

\section{Holidays}
\input{"holidays/apple matzo charlotte"}
\input{holidays/stuffing}
\input{"holidays/cranberry sauce"}
\input{holidays/eggnog}
\input{"holidays/orange tofu"}
balsamic-honey reduction, (Christmas 2016)
kugel quiche (Passover 2018)
spinach matzo pie (Passover 2014?)
charosets
Phil’s matzo ball soup (P)

\section{Desserts}
Biscotti
Creme Brulee
\input{dessert/dustin}
\input{dessert/"watergate cake"}
chocolate caramel matzo
ginger spice cake
triple chocolate cookies
ginger cookies from Cooks Illustrated
gingerbread
snickerdoodles from SE
caramel/custard/butterscotch
buttercream icing from Madhu?
Bruce's pecan pie
Lemon poppyseed loaf (Madhu)

\section{Fermenting \& Extracting}
harissa
pickles?
bitters?
homebrew recipes??? cocktails?

\section{Menus}
\input{menus}

\section{Our Parents' Cooking}
The following recipes are more faithful to the originals than the preceding ones; for example, sugar quantities have been left as-is, rather than halved as I would. Commentary is indicated by [].

I was sent off to college with my parents' copy of Joy of Cooking, ca. 1975 (a wedding gift), including recipes clipped out of newspapers and jotted down on used UW punchcards. Here are some Bieber family essentials, from Joy itself and the enclosed ephemera.
\input{bieber}

When Daniel and I had our !wedding, the Bergeys presented us with a binder to store recipes, pre-populated with favorites from every family member and childhood delights.
% \input{bergey}

Daniel's 6th grade class put together a cookbook featuring recipes from every family, painstakingly handwritten and photocopied. For posterity, here they are.
% \input{kidscancook}

\printindex
\end{document}
