\begin{recipe}{Double Chocolate Cookies}{mixer \hfill 350\0F \hfill 10 min.}{\textbf{Source:} Cook's Illustrated \hfill makes 30}

 \freeform Every year I bake a few batches of cookies for the winter holidays. This is one of my go-to recipes.

 \ing[2]{cups}{flour}
 \ing[\fr12]{cup}{Dutch cocoa}
 \ing[2]{tsp.}{baking powder}
 \ing[1]{tsp.}{salt}
 Sift together dry ingredients in a medium bowl.

 \ing[16]{oz.}{semisweet chocolate}
 Melt the chocolate in the microwave, stirring frequently. Set aside.

 \ing[4]{}{eggs}
 \ing[2]{tsp.}{vanilla}
 \ing[2]{tsp.}{espresso powder}
 Lightly beat the eggs and vanilla in a small bowl. Sprinkle with the coffee powder and set aside.

\ing[10]{tbsp.}{butter}
 \ing[1\fr12]{cups}{brown sugar}
 \ing[\fr12]{cup}{sugar}
 Beat butter until smooth and creamy. Add sugars, then eggs, then chocolate, beating well between additions. Add dry ingredients and mix on low just until combined---less than a minute.

 \newstep Cover bowl with plastic wrap and let stand 30 min.

 \newstep Preheat oven to 350\0F and grease or line two cookie sheets. Scoop dough by heaping tablespoons 1\fr12\inch\ apart.

 \newstep Bake cookies until the edges are set and the centers are soft, about 10 min. Switch the cookie trays halfway through baking. Cool on trays for 10 minutes, then move onto cooling racks.

\end{recipe}

% \begin{recipe}{Gingerbread}{%equipment \hfill %temperature \hfill %time}{\textbf{Source:} \hfill serves %n}
% \end{recipe}

\begin{recipe}{Molasses Cookies}{mixer \hfill 375\0F \hfill 10 min.}{\textbf{Source:} Cook's Illustrated \hfill makes 24}

 \freeform It's a bit of a production to roll the cookies in sugar, but it's worth it to get that crinkly outside. At least you didn't have to use a rolling pin.

 \ing[2\fr14]{cups}{flour}
 \ing[1\fr12]{tsp.}{cinnamon, ground}
 \ing[1\fr12]{tsp.}{ginger, ground}
 \ing[\fr12]{tsp.}{cloves, ground}
 \ing[\fr12]{tsp.}{allspice, ground}
 \ing[\fr14]{tsp.}{black pepper, ground}
 \ing[1]{tsp.}{baking soda}
 \ing[\fr12]{tsp.}{salt}
 In a medium bowl, stir together dry ingredients.

 \ing[12]{tbsp.}{butter, softened}
 \ing[\fr13]{cup}{white sugar}
 \ing[\fr13]{cup}{brown sugar}
 Beat the butter and sugars together until light and fluffy.

 \ing[1]{}{egg}
 \ing[1]{tsp.}{vanilla}
 \ing[\fr12]{cup}{molasses}
 Add egg and vanilla, then molasses, mixing thoroughly between additions. Reduce speed to low and add dry ingredients, scraping the sides to mix well.

 \newstep Roll dough into balls and dip in white sugar. Set them 2\inch\ apart on a greased cookie sheet.

 \newstep Bake 1 sheet at a time until cookies are puffy and edges are set, about 10 min. Rotate the cookie tray halfway through baking. Do not overbake! Cool on trays for 5 minutes, then move onto cooling racks.
\end{recipe}

\begin{recipe}{Snickerdoodles}{mixer \hfill 400\0F/350\0F \hfill 10 min.}{\textbf{Source:} \href{https://www.seriouseats.com/recipes/2016/01/new-fashioned-snickerdoodle-cookie-recipe.html}{Serious Eats} \hfill makes 24}
 \freeform What can I say, I love a cookie with a chewy center and crisp edges. The coconut oil makes these subtly different and really delicious.

 \ing[4]{oz.}{butter}
 \ing[3]{oz.}{virgin coconut oil}
 \ing[10\fr12]{oz.}{sugar}
 \ing[1\fr14]{tsp.}{kosher salt}
 \ing[1]{tsp.}{baking powder}
 \ing[1]{tbsp.}{vanilla}
 Mix butter, coconut oil, sugar, salt, baking powder, and vanilla on low, then medium, until the mixture is soft, fluffy, and pale.

 \ing[1]{}{egg}
 Add the egg and continue beating until smooth. Scrape the bowl as necessary.

 \ing[10\fr12]{oz.}{flour}
 Reduce speed to low and add the flour, mixing to form a stiff dough.

 \ing[2]{oz.}{sugar}
 \ing[2\fr34]{tsp.}{cinnamon, ground}
 \ing[1\fr12]{tsp.}{cinnamon, grated}
 Mix sugar and cinnamons in a small bowl. Roll 2 tbsp.\ of dough into a ball, roll in the cinnamon sugar, then flatten on a greased baking tray, leaving 1\fr12\inch\ between cookies. Optionally, sprinkle the remaining cinammon sugar on top for extra crinkly cookies.

 \newstep Bake at 400\0F until the cookies spread, about 5 min., then reduce the temperature to 350\0F. Continue baking until firm around the edges and soft in the middle, 5--6 min.\ longer. Cool at least 10 min.\ on the tray, then move onto cooling racks.
\end{recipe}
