\begin{recipe}[Nanaimo]{Nanaimo Bars}{food processor, 8\inch\X8\inch baking dish \hfill 350\0F \hfill 15 min.}{\textbf{Source:} adapted from \href{https://www.humblebeeandme.com/totally-from-scratch-nanaimo-bars/}{Humblebee \& Me} and \href{https://www.rockrecipes.com/chocolate-mint-nanaimo-bars/}{Rock Recipes}\hfill serves 25}

 \freeform This recipe abandons the 100\% stovetop nature of the traditional Nanaimo bar, but I think it's worth it. Key features: toasted nuts \& coconut, a thicker cookie layer, a custard layer without custard powder, and a chocolate topping that's sliceable right out of the fridge!

 \ing[1]{cup}{flaked unsweetened coconut}
 \ing[\fr12]{cup}{almonds}
 Toast the coconut and almonds at 350\0F, stirring every 5 minutes until they smell delicious.

 \ing[\fr12]{cup}{butter}
 Put the butter in the food processor and pour the hot almonds and coconut directly on top. Pulse a few times to melt the butter.

 \ing[1\fr12]{cups}{graham cracker crumbs}
 \ing[\fr14]{cup}{white sugar}
 \ing[5]{tbsp}{cocoa powder}
 \ing[\fr14]{tsp}{salt}
 \ing[1]{}{egg}
 Add the remaining ingredients. Pulse a few more times to combine.

 \newstep Press the crust into the greased baking dish and bake at 350\0F for 15 minutes.

 \ing[4]{tbsp}{cornstarch}
 \ing[1]{cup}{whole milk}
 \ing[1]{cup}{heavy cream}
 \ing[2]{tsp}{vanilla extract}
 In a small bowl, mix half a cup of milk with the cornstarch. Heat the remaining milk and cream until steaming, not boiling. Stir in the vanilla.

 \ing[4]{}{eggs}
 \ing[\fr12]{cup}{sugar}
 \ing[]{pinch}{salt}
 In a bowl, whisk the eggs and sugar and salt. Add the hot milk to the eggs, stirring it in one spoonful at a time until the eggs are warm.

 \newstep Pour the tempered eggs back into the saucepot, and heat on low, stirring constantly, until the custard starts to thicken. Stir the cornstarch slurry and add it quickly, continuing to stir, especially in the corners, to produce an extremely thick custard.

 \newstep Let the custard cool slightly, then spread it over the baked crust. Set aside to cool.

 \ing[6]{oz.}{bittersweet chocolate}
 \ing[\fr12]{cup}{heavy cream}
 Heat the cream and chocolate on low, stirring constantly, until the chocolate starts to melt. Turn off the heat and keep stirring, until the ganache is smooth and glossy.

 \newstep Spread the chocolate over the custard, smoothing it as best you can. Chill, slice, and serve.

 \freeform Notes:
 \begin{itemize}
  \item  If you use the baking dish to toast the nuts and coconut, you won't have to grease it! But you can if you want to, or add a layer of foil.
  \item Custard is tricky; feel free to turn the stove off if you feel it's going too fast. If your custard curdles, feel free to sieve it or just go with it--it'll be delicious either way.
  \item To make these mint instead of vanilla, use 1 tsp.\ mint extract and 10--15 drops green food coloring.
  \item Since these are very rich and prone to squishing, cut them into bite-size pieces--5\X5 or even 6\X6 if you can manage it.
  \item TODO: figure out an all-cornstarch or all-custard powder custard layer; also this makes too much, too thick custard??
 \end{itemize}
\end{recipe}
