\begin{recipe}{Eggnog I}{large bowl, mixer \hfill chill after mixing \hfill 30 min.}{\textbf{Source:} Prof.\ Serge Lang, Princeton University \hfill serves 12}
 % tags: Thanksgiving, recipe

 \freeform This epic libation was reconstructed by Phil Bergey at Thanksgiving 2018.

 \ing[12]{} {eggs, separated}
 Separate the eggs; put the yolks into a large serving bowl and the whites into a mixer bowl.

 \ing[1] {lb.} {sugar}
 \ing[2] {qt.} {milk}
 \ing[1] {qt.} {heavy cream}
 \ing[700] {mL} {Remy Martin VSOP cognac}
 Mix the sugar, milk, and cream into the egg yolks, then add the cognac.

 \ing[12]{} {egg whites}
 Whip the egg whites and fold gently into the eggnog.

 \ing{}{nutmeg}
 Grate nutmeg over top, stir gently, and serve.

 \freeform Notes:
 \begin{itemize}
  \item Ingredients should be chilled before starting, and the finished eggnog should be kept cool; no one likes warm eggnog.
 \end{itemize}

\end{recipe}

\begin{recipe}{Eggnog II}{stand mixer \hfill chill after mixing \hfill 30 min.}{\textbf{Source:} Alton Brown \hfill serves 4}
 % tags: Thanksgiving
 \freeform At Thanksgiving 2019, Phil presented this alternative eggnog, made in advance.

 \ing[4]{} {eggs, separated}
 \ing[\fr{13}]{cup}{sugar}
 In the bowl of a stand mixer, beat together egg yolks and sugar until the yolks lighten in color and the sugar is completely dissolved.

 \ing[1]{pint}{whole milk}
 \ing[1]{cup}{heavy cream}
 \ing[1\fr{14}]{oz.}{bourbon}
 \ing[1\fr{14}]{oz.}{dark rum}
 \ing[1]{tsp.}{nutmeg, freshly grated}
 Add the milk, cream, bourbon, rum, and nutmeg. Stir to combine.

 \ing[4]{}{egg whites}
 \ing[1]{tbsp.}{sugar}
 Beat egg whites to soft peaks. While mixing, add the sugar and beat until stiff peaks form.

 \newstep Gently fold egg whites into the eggnog. Chill and serve.

 \freeform Notes:
 \begin{itemize}
  \item Alton Brown makes no recommendations as to the bourbon; Phil chose to make this with Smith \& Cross Traditional Jamaican Rum and Bulleit 90 Proof Bourbon.
 \end{itemize}
\end{recipe}
