\begin{recipe}{Spinach Matzo Pie}{9\inch\X13\inch baking dish \hfill 400\0F \hfill 30--35 min.}{\textbf{Source:} Melissa Roberts, \href{https://www.epicurious.com/recipes/food/views/spinach-and-matzoh-pie-242019}{\textit{Gourmet}, April 2008} \hfill serves 8--12}
 \freeform This is a contender for best vegetarian Passover entree. There's matzo right in the name, how can you beat that? But honestly, this matzo lasagna concept is presumably a whole genre, we just haven't looked past this spanakopita-inspired dish.

 \ing[16]{oz.}{cottage cheese}
 \ing[2]{cups}{whole milk}
 \ing[3]{}{eggs}
 \ing[\fr14]{tsp.}{nutmeg, grated}
 In a large bowl or blender, puree the cottage cheese, milk, eggs, and nutmeg.

 \ing[6]{}{matzos}
 Place matzos in a 8\inch\X8\inch baking dish and pour cottage cheese mixture over to cover. Let sit 15 min.\ until matzo have softened.

 \ing[1]{med.}{onion, chopped}
 \ing[3]{tbsp.}{olive oil}
 Saute the onion in the olive oil until golden, 12--15 min.

 \ing[20]{oz.}{spinach, thawed}
 Press the spinach in a sieve to remove as much water as possible. Add it to the fried onion and saute 5 min.

 \ing[\fr13]{cup}{dill, chopped}
 \ing[\fr34]{tsp.}{salt}
 \ing[\fr12]{tsp.}{pepper}
 Remove spinach from heat and stir in dill, salt, and pepper.

 \ing[1]{cup}{feta, crumbled}
 Combine the remaining cottage cheese mixture and feta with the spinach.

 \ing[\fr12]{cup}{feta, crumbled}
 Grease a 9\inch\X13\inch baking dish and place two softened matzos in the bottom. Spread half the spinach filling over them, then cover with two more matzos. Repeat with the rest of the spinach and top with the last two matzos. Pour any cottage cheese mixture that remains from soaking over top. Sprinkle with feta.

 \ing[2]{tbsp.}{dill, chopped}
 Bake, uncovered, until golden and set. Cool 10 min., then sprinkle with dill and serve.

 \freeform Notes:
 \begin{itemize}
  \item This dish can be assembled ahead of time, chilled and covered until ready to bake. Add 10--15 min.\ cooking time and follow your nose.
 \end{itemize}
\end{recipe}
