\begin{recipe}{Bread Stuffing}{food processor, 9\inch\X13\inch baking dish \hfill 350\0F \hfill 30--60 min.}{\textbf{Source:} Chutatip `Nok' Suntaranon, \href{https://www.kalaya.net/}{Kalaya Thai Kitchen} \hfill serves 8}
 \freeform A good sausage stuffing recipe, veganized.

 \ing[4]{stalks}{celery}
 \ing[2]{med.}{carrots}
 \ing[1]{med.}{onion}
 \ing[1--2]{cloves}{garlic}
 In a food processor, finely chop the celery, carrots, onion, and garlic. Set aside.

 \ing[12]{oz.}{chestnuts, raw}
 If using raw chestnuts: blanch and peel. Coarsely chop 6--7 oz.\ chestnuts, retaining a few whole chestnuts for garnish.

 \ing[6]{slices}{vege bacon, chopped}
 Saute the bacon in a large skillet over high heat, in olive oil. Remove the bacon and reserve for garnish, leaving the oil in the pan.

 \ing[1]{tbsp.}{butter}
 \ing[10]{oz.}{mushrooms, chopped}
 \ing[1]{lb.}{sweet Italian seitan, crumbled}
 \ing[1]{lb.}{hot Italian vege sausage}
 Return the skillet to medium heat and add butter. Saute the chopped aromatics until softened and fragrant, 3--5 minutes. Add the mushrooms and saute until they release their liquid, 5 min. Add the sausage bits and saute over high heat, smashing them into smaller chunks, until liquid has been absorbed and browning has started, 10--15 min. Stir frequently and add oil as needed.

 \ing[12]{oz.}{bread crumbs}
 \ing[2+]{cups}{vegetable stock}
 \ing[1]{cup}{dried cranberries}
 \ing[7]{oz.}{chestnuts, chopped}
 Remove skillet from heat and add bread crumbs, 2 cups stock, and dried cranberries. Stir and toss to combine. Season with salt and pepper, then fold in chestnuts. Transfer to a baking dish and refrigerate for up to 2 days. (Stuffing may be frozen at this point, and thawed before continuing.)

 \ing[1]{bunch}{parsley, chopped}
 Mix the parsley into the stuffing; reserve a handful for garnish. Add salt, pepper, and stock to taste. Bake until hot in the middle and browned on top. Stuffing may be held at 200\0F until serving.

 \newstep Garnish with reserved chestnuts, bacon bits, fresh cranberries, sprigs of parsley, rosemary, thyme, lavender, and marigold petals.

 \freeform Notes:
 \begin{itemize}
  \item We doubled this recipe for Thanksgiving 2019 and it yielded way too much stuffing. Beware.
  \item We used \href{https://www.uptonsnaturals.com/products/italian-seitan}{Upton's Naturals Italian Seitan} and \href{https://www.beyondmeat.com/products/hot-italian/}{Beyond Sausage Hot Italian Sausage}. Removing the sausage casings is a bit of a faff. Field Roast \href{https://fieldroast.com/product/italian-sausage/}{Italian}, \href{https://fieldroast.com/product/mexican-chipotle-sausage/}{Mexican Chipotle}, and/or \href{https://fieldroast.com/product/smoked-apple-sage-sausage/}{Apple Sage} Sausage would probably suit, or skip right to something already crumbled.
  \item Hazelnuts make a delightful replacement for some or all of the chestnuts.
  \item We skipped most of the garnishes and it was ok. I would try this again with better presentation and bread chunks instead of crumbs.
 \end{itemize}
\end{recipe}

\begin{recipe}{Cornbread Stuffing}{}{}
 \freeform Historically, Christalee's family makes a cornbread stuffing, with mushrooms, peppers, kielbasa, and sage. Eventually she might find the recipe and put it here.
\end{recipe}
