\begin{recipe}{Black Pepper Tofu}{wok \hfill stovetop \hfill}{\textbf{Source:} \textit{Plenty}, via \href{https://smittenkitchen.com/2019/08/black-pepper-tofu-and-eggplant/}{Smitten Kitchen} \hfill serves 4--6}
  \freeform We usually cook this for Thanksgiving, when the oven is in high demand, so it's convenient to cook it entirely in the wok. See Notes for a sheet pan variation.

\ing[14]{oz.}{firm tofu (1 block)}
Chop tofu into \fr{12}\inch\ cubes. Fry tofu in \fr{18}\inch\ oil, in 2 batches, until golden but not crisp.

\ing[\fr{34}-1]{lb.}{eggplant}
Chop eggplant into 1\inch\ chunks. Fry eggplant in 2--3 batches until just tender.

\ing[1]{med.}{onion}
\ing[5]{cloves}{garlic, chopped}
\ing[2]{tbsp.}{ginger, chopped}
\ing[2--3]{}{fresh or dried chilis}
\ing{}{(serrano, cayenne, arbol)}
Reheat wok and add 2 tbsp. oil. Saute aromatics until shiny and soft.

\ing[1\fr{12}]{tbsp.}{kecap manis*}
\ing[1\fr{12}]{tbsp.}{light soy sauce or shoyu}
\ing[2]{tsp.}{dark soy sauce}
\ing[1]{tbsp.}{white sugar}
\ing[2]{tbsp.}{ground black pepper}
Add soy sauces, sugar, and black pepper. Stir to combine.

\ing[4--8]{}{scallions}
Chop scallions to 1\inch\ lengths. Warm tofu and eggplant in sauce 1 min. Stir in scallions, and serve.

  \freeform Notes:
  \begin{itemize}
    \item To make this in the oven, preheat to 425\0F.
    \item Spread eggplant and tofu on a baking sheet with 2--4 tbsp. oil. Roast 20 min., stir, then roast 10 min. more.
    \item Continue with recipe as written from step 2.
    \item If you don't have kecap manis, use 2\fr{12}\ tbsp. light soy sauce and 4 tsp. dark soy sauce total.
  \end{itemize}
\end{recipe}