\begin{recipe}{Caramel Tofu}{}{\textbf{Source:} \textit{How to Cook Everything Vegetarian} \hfill serves 4}
  \freeform Fast, unusual, delicious - and easy, once you get the hang of caramelizing sugar. I promise, it's not hard! Just keep an eye on the sugar and when in doubt, take it off the heat.

\ing[\fr{12}]{cup}{white sugar}
Heat the sugar in a pot large enough to hold the tofu. Shake the pan gently as the sugar heats and liquefies. When it starts to darken, take it off the heat.

\ing[\fr{14}]{cup}{soy sauce*}
\ing[\fr{14}]{cup}{water}
Stand back and add the water and soy sauce to the pan. It will bubble up aggressively! Don't panic.

\newstep Turn the heat back on to medium-high. Cook, stirring constantly, until caramel is dissolved.

\ing[2]{}{scallions}
Chop the scallions into 1--2\inch\ lengths and add them to the sauce. Cook 5 min. until they soften.

\ing[1]{tsp.}{black pepper, freshly ground}
\ing[2]{tbsp.}{lime juice*}
\ing[14]{oz.}{tofu (1 block), cubed}
Add the pepper and lime juice, then add the tofu. Stir gently and simmer 5 min. until tofu is slightly swollen. Correct seasoning and serve.

\freeform Notes:
\begin{itemize}
  \item If you want to get fancy, use this mixture instead of the soy sauce: 1 tbsp. soy sauce, 1 tbsp. water, 4 tbsp. lime juice, 1\fr{12} tsp. brown sugar, 1 clove minced garlic. Later in the recipe, add lime juice to taste, starting with 1 tbsp.
  \item Once you've gotten comfortable with caramel, let it darken a bit before turning it off---but always remember it will continue cooking after you take it off the stove, so don't let it go too long!
  \item If you do ruin the caramel, try boiling water in the pot to clean it before you break out the scouring pad.
  \item Although it won't be crispy after braising, this sauce can be used with fried tofu as well.
\end{itemize}
\end{recipe}