\begin{recipe}{Italian Tempeh Pasta}{}{\textbf{Source:} \textit{Veganomicon} \hfill serves 4}
  \freeform This magical recipe is a bit fussy, but it's worth it to get tempeh reminiscent of Italian sausage, paired with broccoli rabe and whole wheat pasta.

\ing[\fr{12}]{cup}{vegetable stock}
\ing[2]{tbsp.}{soy sauce}
\ing[2]{tbsp.}{tomato paste}
\ing[1]{clove}{garlic}
\ing[1]{tbsp.}{fennel seed}
\ing[1]{tsp.}{red pepper flakes}
\ing[1\fr{12}]{tsp.}{oregano}
Combine marinade ingredients in a measuring cup.

\ing[8]{oz.}{tempeh (1 block)}
Chop tempeh into cubes and dump into a skillet. Pour the marinade over it and stir to coat. Cook over medium heat until liquid reaches a simmer, then cover and steam for 8 min. or liquid is absorbed and tempeh is tender. Stir a few times while tempeh is steaming.

\newstep Transfer half the tempeh to a large serving bowl and crumble with the back of a spoon. Add the rest of the tempeh on top and wash the skillet out.

\ing[2]{tbsp.}{olive oil}
Heat oil to medium in the clean skillet. Add the tempeh cubes and crumbles and stir fry for 5 min. until they start to brown. Return to serving bowl and set aside.

\ing[\fr{12}]{lb.}{whole wheat rotelle}
Cook the pasta as directed in lightly salted water. Drain and toss with olive oil if other ingredients aren't ready yet.

\ing[\fr{14}]{cup}{olive oil}
\ing[5]{cloves}{garlic}
Heat oil in the skillet and add the sliced garlic. Once it starts to sizzle, cook for about 1 min. Do not burn!

\ing[1]{bunch}{broccoli rabe*}
\ing[2--3]{tbsp.}{white wine, water, or stock}
Add the broccoli rabe, stir to coat with oil, sprinkle with salt, and cook, covered, for 2 min. Add 2 tbsp. liquid and cover again; steam for 8--10 min. until stems are tender.

\ing[2]{tsp.}{red wine vinegar or balsamic vinegar}
Saute broccoli rabe uncovered until liquid has evaporated. Combine with pasta and tempeh, sprinkle with vinegar, salt and pepper to taste, and serve.
\end{recipe}